%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {INSERM -- CRCI\textsuperscript{2}NA, Nantes - Angers Cancer and Immunology Research Center} % Organization
    {Postdoctoral Researcher} % Job title
    {Nantes, France} % Location
    {Since Jan. 2023} % Date(s)
    {
	Mentor: Dr. Éric Letouzé (team ICAGEN, CRCI\textsuperscript{2}NA, INSERM).
    \vspace{0.5cm}
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Integrate whole-genome and single-cell multiomic datasets from a cohort of 40 multiple myeloma patients.}
		\item {Identify features for patient stratification and treatment susceptibility.}
		\item {Develop, maintain, and deploy pipelines for the analyses of single-cell multiomic data.}
		\item {Design integration strategies to uncover tumor clonal history from genetic, epigenetic and functional data.}
	\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Integrative Phenomics,  a French R\&D company on human microbiome health} % Organization
    {Research Scientist / Data Scientist (Industry position)} % Job title
    {Paris, France} % Location
    {Apr. 2020 - Jun. 2022} % Date(s)
    {
    Collaborator: Dr. Eugeni Belda (Data Scientist, Integrative Phenomics)
    \vspace{0.5cm}
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed pipelines for NGS analysis of gut metagenomic data and deployed them on the cloud.}
		\item {Designed and implemented an innovative modeling platform to predict how food metabolites interact with a patient's microbiote.}
		\item {Analyzed blood and stool metabolomics data to validate model predictions.} 
		\item {Produced regular scientific reports, co-wrote publications, and animated internal/external meetings.}
		\item {Co-wrote public grant applications and gave multiple scientific presentations in front of the press and investors.}
	\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CNRS -- Université de Nantes, Laboratory of Digital Sciences of Nantes} % Organization
    {Postdoctoral Researcher} % Job title
    {Nantes, France} % Location
    {Jan. 2018 - Dec. 2019} % Date(s)
    {
	Mentor: Dr. Samuel Chaffron (team COMBI, LS2N, CNRS).
    \vspace{0.5cm}
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed pipelines for NGS analysis of ocean metaomics data and deployed them on a cluster.}
		\item {Implemented network reconstruction/clustering methods on Tara expeditions metagenomic and metatranscriptomic datasets.}
		\item {Implemented metabolic reconstruction/simulation methods on communities of co-active and co-occurring microbes.}
		\item {Co‑wrote and obtained a public grant for a 6‑month extension of a Postdoc fellowship.}
		\item {Co-wrote publications and talked at multiple scientific events.}
	\end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Inria -- Université Grenoble Alpes, Project-team Ibis \& Laboratoire Interdisciplinaire de Physique} % Organization
    {Research and Teaching Assistant, PhD Student} % Job title
    {Grenoble, France} % Location
    {Sep. 2012 - Mar. 2017} % Date(s)
    {
	Supervisors: Dr. Hidde de Jong (Project-team Ibis, Inria) \& Pr. Johannes Geiselmann (team BIOP, LIPhy).
    \vspace{0.5cm}
	\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Constructed an abstract mathematical model of nutrient allocation in microorganisms.}
        \item {Applied Optimal Control methods to predict optimal nutrient allocations during an environmental change.}
        \item {Compared the identified optima with known regulatory processes of nutrient allocation in E. \textit{coli}.}
		\item {Validated the predicted optima by engineering bacteria with fluorescent ribosomes and monitoring them in a microfluidic device.}
		\item {Wrote an extensive thesis manuscript, co-wrote publications, and talked at multiple scientific events.}
	\end{cvitems}
    }
\end{cventries}    

\cvsubsection{Internships}

\begin{cventries}
%------------------------------------------------
  \cventry
    {Inria -- Sensitivity analysis for a complex model of the gene expression machinery in E. \textit{coli}} % Organization
    {Research Assistant, Intern} % Job title
    {Grenoble, France} % Location
    {Feb.-Jun. 2012} % Date(s)
    {
    Supervisors: Dr. Hidde de Jong \& Dr. Delphine Ropers (Project-team Ibis, Inria).
    }
    
%------------------------------------------------
  \cventry
    {University of Cambridge -- Theoretical study of the evolution towards multicellularity in microalgae} % Organization
    {Research Assistant, Intern} % Job title
    {Cambridge, United Kingdom} % Location
    {Feb.-Jun. 2011} % Date(s)
    {
	Supervisor: Pr. Raymond E. Goldstein (Department of Applied Mathematics and Theoretical Physics).
    }
    
%------------------------------------------------
  \cventry
    {École Normale Supérieure -- Dynamical responses of oscillating yeast cell suspensions to periodic forcing} % Organization
    {Research Assistant, Intern} % Job title
    {Paris, France} % Location
    {Jun.-Jul. 2010} % Date(s)
    {
	Supervisor: Dr. Silvia de Monte (Eco-evolutionary Mathematics, IBENS).
    }

\end{cventries}
